---
title: "Mall Customer Segmentation"
execute: 
  echo: false
---

## Introduction
Customer segmentation is a key marketing strategy that involves dividing a company's customer base into distinct groups of individuals that share similar characteristics. This was sourced from a dataset that had basic original mall customer information. The data was filtered and selected to show the relationship between age, gender, Income, and spending score which would possibly become useful for businesses to make the market more effective. The visualizations reveal distinct patterns in age, income, spending behavior, and gender distribution, providing valuable insights for customer segmentation and targeted marketing strategies.


## Data Models

The plots below analyze mall customer information, offering insights for brands and companies to enhance marketing efficiency and boost profitability. By understanding customer behavior and preferences, businesses can tailor their strategies, optimize their campaigns, and achieve better results, ultimately leading to increased revenue and customer satisfaction.

```{r}
#| message: false
#| label: setup

library(tidyverse)
library(scales)
library(plotly)
```

This graph identifies the predominant age groups of frequent mall customers, offering valuable insights for businesses and marketing firms to refine their audience targeting strategies.
```{r}
#| message: false
#| warning: false

plot1 <- read_csv("/Users/neera/OneDrive/Documents/Desktop/projects/Customer_Segmentation/Mall_Customers.csv") |>
  drop_na() |>
  ggplot(aes(x = Gender,
             y = Age, 
             fill = Gender)) +
  geom_boxplot(width = 3) +
  geom_violin(alpha = 0.5,
              width = 0.1) +
  scale_y_continuous(limits = c(10, 70), 
                     breaks = seq(10, 70, by = 10)) +
  theme_minimal() +
  labs(title = "Age Distribution by Gender Among Mall Customers",
       subtitle = "Analysis of Age Variations within Gender Groups",
       x = "Gender",
       y = "Age",
       caption = "Source: Mall Customers Dataset") +
  theme(
    plot.title = element_text(size = 16,
                              face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10))

interactive_plot <- ggplotly(plot1)

interactive_plot
```

This histogram presents the same data as the previous graph but offers a clearer view of the number of frequent age groups.
```{r}
#| warning: false

x <- read_csv(file = "Mall_Customers.csv", 
              show_col_types = FALSE) |>
     drop_na()
plot <- x |>
  ggplot(aes(x = Age,
             fill = Gender, 
             color = Gender)) +
  geom_histogram(alpha = 0.5) +
  theme_minimal() +
  labs(
    title = "Age Distribution by Gender",
    x = "Age",
    y = "Count",
    fill = "Gender",
    color = "Gender"
  )

# Convert to an interactive plot
interactive_plot <- ggplotly(plot)

interactive_plot
```

