---
title: "Mall Customer Segmentation"
execute: 
  echo: false
---
Analyzing information of Mall Customers to provide insights to Brands and other companies on Improving their marketing efficiency and increasing profitability.


## Introduction
Customer segmentation is a key marketing strategy that involves dividing a company's customer base into distinct groups of individuals that share similar characteristics. These characteristics can include demographic factors (age, gender, income), behavioral patterns (purchase history, brand loyalty), psychographics (lifestyle, values), and geographic information (location).

By identifying these segments, businesses can tailor their marketing efforts, product development, and customer service to better meet the specific needs and preferences of each group. This targeted approach helps in improving customer satisfaction, enhancing marketing effectiveness, and increasing overall profitability.


# Data Models

The below plot shows the data on Mall Customers and their ages. 
With this data, businesses can find out what kind products to sell for the age group that most 6 visits the Mall.

```{r}
#| message: false
#| label: setup

library(tidyverse)
library(scales)
library(plotly)
```

```{r}
#| message: false
#| warning: false

plot1 <- read_csv("/Users/neera/OneDrive/Documents/Desktop/projects/Customer_Segmentation/Mall_Customers.csv") |>
  drop_na() |>
  ggplot(aes(x = Gender, y = Age, fill = Gender)) +
  geom_boxplot(width = 3) +
  geom_violin(alpha = 0.5,
              width = 0.1) +
  scale_y_continuous(limits = c(10, 70), 
                     breaks = seq(10, 70, by = 10)) +
  theme_minimal() +
  labs(title = "Age Distribution by Gender Among Mall Customers",
       subtitle = "Analysis of Age Variations within Gender Groups",
       x = "Gender",
       y = "Age",
       caption = "Source: Mall Customers Dataset") +
  theme(plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10))

interactive_plot <- ggplotly(plot1)

interactive_plot
```


```{r}
#| warning: false

x <- read_csv(file = "Mall_Customers.csv", show_col_types = FALSE)

# Create a histogram
plot <- x |>
  ggplot(aes(x = Age, fill = Gender, color = Gender)) +
  geom_histogram(alpha = 0.5) +
  theme_minimal() +
  labs(
    title = "Age Distribution by Gender",
    x = "Age",
    y = "Count",
    fill = "Gender",
    color = "Gender"
  )

# Convert to an interactive plot
interactive_plot <- ggplotly(plot)

interactive_plot
```

