---
title: "Visual Analysis"
execute: 
  echo: false
---

## Central Question
How can we segment mall customers based on their purchasing behaviour, gender, age, and annual income to make brands and companies target customers more efficiently  


## Visual Representation
```{r}
#| message: false
#| label: setup

library(tidyverse)
library(scales)
library(plotly)
```

```{r}
#| message: false
#| warning: false
plot4 <- read_csv("/Users/neera/OneDrive/Documents/Desktop/projects/Customer_Segmentation/Mall_Customers.csv") |>
  drop_na() |>
  ggplot(aes(x = Age,
             y = `Annual Income (k$)`)) +
  geom_point() +
  geom_smooth(method = 'loess',  
              se = FALSE,
              formula = y ~ x) +
  theme_minimal() +
  labs(title = "Relationship Between Age and Annual Income",
       x = "Age (Years)",
       y = "Annual Income (in $1000s)",
       caption = "Source: Mall Customers Dataset")

# Convert to interactive plot
interactive_plot <- ggplotly(plot4)  # Changed to plot4
interactive_plot
```

```{r}
#| warning: false
#| message: false

plot3 <- read_csv("/Users/neera/OneDrive/Documents/Desktop/projects/Customer_Segmentation/Mall_Customers.csv") |>
  drop_na() |>
  ggplot(aes(x = `Annual Income (k$)`,
             y = `Spending Score (1-100)`, 
             color = Gender)) +
  geom_density_2d() + 
  geom_point(alpha = 0.5) +
  scale_x_continuous(limits = c(20, 140),
                     breaks = seq(20, 140, by = 20)) +
  labs(
    title = "Relationship between Annual Income \nand Spending Score",
    x = "Annual Income (k$)",
    y = "Spending Score (1-100)",
    caption = "Data Source: Mall_Customers.csv"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.title = element_text(face = "bold")
  )

# Convert to interactive plot
interactive_plot <- ggplotly(plot3)
interactive_plot
```

```{r}
#| warning: false
#| message: false

plot5 <- read_csv("Mall_Customers.csv") |>
  drop_na() |>
  select(`Spending Score (1-100)`,
         Age)

plot <- ggplot(plot5, aes(x = Age, 
                          y = `Spending Score (1-100)`)) +
  geom_point(color = 'blue',
             alpha = 0.6) +
  geom_density2d(color = 'red') +
  geom_smooth(method = 'loess',
              se = FALSE, 
              color = 'green') +
  scale_y_continuous(limits = c(0, 100), 
                     breaks = seq(0, 100, by = 20)) +
  labs(
    title = "Age vs. Spending Score",
    subtitle = "Analyzing the spending behavior across different age groups",
    x = "Age",
    y = "Spending Score (1-100)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

interactive_plot <- ggplotly(plot, tooltip = c("x", "y"))

interactive_plot
```

```{r}
#| warning: false
#| message: false

data <- read_csv("Mall_Customers.csv") |>
  drop_na() |>
  mutate(High_Spenders = ifelse(`Spending Score (1-100)` >= 80,
                                `Spending Score (1-100)`, NA),
         Low_Spenders = ifelse(`Spending Score (1-100)` <= 40,
                               `Spending Score (1-100)`, NA), 
         Medium_Spenders = ifelse(`Spending Score (1-100)` <= 80 & `Spending Score (1-100)` >= 40,
                                  `Spending Score (1-100)`, NA))


plot6 <- data |>
  ggplot() +
  geom_point(aes(x = Age, y = High_Spenders),
             color = 'red',
             size = 1) +
  geom_point(aes(x = Age, y = Low_Spenders),
             color = 'green', 
             size = 1) +
  geom_point(aes(x = Age, y = Medium_Spenders), 
             color = 'blue', 
             size = 1) +
  scale_y_continuous(limits = c(20, 100),
                     breaks = seq(20, 100, by = 20)) +
  labs(
    title = "Spending Scores by Age Group",
    subtitle = "High, Medium, and Low Spenders",
    caption = "Source: Mall Customers Dataset",
    x = "Age",
    y = "Spending Score (1-100)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, face = "italic", hjust = 0.5),
    plot.caption = element_text(size = 10, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

interactive_plot <- ggplotly(plot6, tooltip = c("x", "y"))

interactive_plot
```


## Conclusion
These visualizations reveal distinct patterns in age, income, spending behavior, and gender distribution, providing valuable insights for customer segmentation and targeted marketing strategies.
