---
title: "Visual Analysis"
execute: 
  echo: false
---

## Central Question
How can we segment mall customers based on their purchasing behaviour, gender, age, and annual income to make brands and companies target customers more efficiently  
\n
\n

# Visual Representation
```{r}
#| message: false
#| label: setup

library(tidyverse)
library(scales)
library(plotly)
```


```{r}
#| message: false
#| warning: false
plot4 <- read_csv("/Users/neera/OneDrive/Documents/Desktop/projects/Customer_Segmentation/Mall_Customers.csv") |>
  drop_na() |>
  ggplot(aes(x = Age,
             y = `Annual Income (k$)`)) +
  geom_point() +
  geom_smooth(method = 'loess',  
              se = FALSE,
              formula = y ~ x) +
  theme_minimal() +
  labs(title = "Relationship Between Age and Annual Income",
       x = "Age (Years)",
       y = "Annual Income (in $1000s)",
       caption = "Source: Mall Customers Dataset")

# Convert to interactive plot
interactive_plot <- ggplotly(plot4)  # Changed to plot4
interactive_plot
```

```{r}
#| warning: false
#| message: false

plot3 <- read_csv("/Users/neera/OneDrive/Documents/Desktop/projects/Customer_Segmentation/Mall_Customers.csv") |>
  drop_na() |>
  ggplot(aes(x = `Annual Income (k$)`,
             y = `Spending Score (1-100)`, 
             color = Gender)) +
  geom_density_2d() + 
  geom_point(alpha = 0.5) +
  scale_x_continuous(limits = c(20, 140),
                     breaks = seq(20, 140, by = 20)) +
  labs(
    title = "Relationship between Annual Income \nand Spending Score",
    x = "Annual Income (k$)",
    y = "Spending Score (1-100)",
    caption = "Data Source: Mall_Customers.csv"
  ) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.title = element_text(face = "bold")
  )

# Convert to interactive plot
interactive_plot <- ggplotly(plot3)
interactive_plot
```

### Different types of Spenders
The below graph represents the different types of spenders and their spending scores.
```{r}
#| warning: false
#| message: false

data <- read_csv("Mall_Customers.csv") |>
  drop_na() |>
  mutate(High_Spenders = ifelse(`Spending Score (1-100)` >= 80,
                                `Spending Score (1-100)`, NA),
         Low_Spenders = ifelse(`Spending Score (1-100)` <= 40,
                               `Spending Score (1-100)`, NA), 
         Medium_Spenders = ifelse(`Spending Score (1-100)` <= 80 & `Spending Score (1-100)` >= 40,
                                  `Spending Score (1-100)`, NA))


plot6 <- data |>
  ggplot() +
  geom_point(aes(x = Age, y = High_Spenders),
             color = '#440154FF',
             size = 1,
             alpha = 0.8) +
  geom_point(aes(x = Age, y = Medium_Spenders), 
             color = '#FDE725FF', 
             size = 1,
             alpha = 0.8) +
  geom_point(aes(x = Age, y = Low_Spenders),
             color = '#21908CFF', 
             size = 1,
             alpha = 0.8) +
  scale_y_continuous(limits = c(20, 100),
                     breaks = seq(20, 100, by = 5)) +
  labs(
    title = "Spending Scores by Age Group",
    subtitle = "High, Medium, and Low Spenders",
    caption = "Source: Mall Customers Dataset",
    x = "Age",
    y = "Spending Score (1-100)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, face = "italic", hjust = 0.5),
    plot.caption = element_text(size = 10, hjust = 1),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

interactive_plot <- ggplotly(plot6, tooltip = c("x", "y"))

interactive_plot
```
Graph Logistics - 

 * The graph visually represents the corellation between spending scores and age, this allows marketing brands to produce products that would drag attention to the minds of these mall customers that fall into specific age groups

 * The purple colored points represent High spenders who have their spending scores above 80

 * The bright yellow points represents Medium spenders who have spending score between 80 and 40

 * The teel colored points represents Low spenders who have spending score below 40

## Conclusion
These visualizations reveal distinct patterns in age, income, spending behavior, and gender distribution, providing valuable insights for customer segmentation and targeted marketing strategies.
